Teaching Dossier

### 2020-02-05 CUT/teaching-philosophy.tex
outside the classroom

\subsection{Outside Lecture}

\subsection{Assessment}

\section{Evaluation of Teaching}
I find feedback on my teaching to be tremendously valuable. It is the easiest way for me to identify potential avenues for improvement, while at the same time motivating me by highlighting strong points of my teaching style. I have organized my evaluations below into two categories: those from students in courses I have taught, and those from peers and teaching professionals observing my lectures.
\subsection{Student Evaluations}
%Chart out survey responses for CO 327 with survey adjectives for context for scores (some here, rest in appendix)
%Student comment strong points
%Student comment targets for change
\subsection{Teaching Observations}
One element of the CUT teaching program I took alongside my PhD was having lectures I give upervised by an expert in teaching working with the university's Centre for Teaching Excellence (CTE). I completed two teaching observations through the program. Below I summarize the feedback I received from these observations.
%highlights from 1st observation
\subsubsection*{First Teaching Observation}
\paragraph{}
My first observation was on the guest lecture I gave for Introduction to Game Theory in Fall $2018$ on Correlated Equilibria. The observation was conducted by Shahrukh Athar, a Graduate Instructional Developer working for the CTE. I have included the relevant sections of the full report in Appendix \ref{sec:observation-report-1}. The feedback in the report was divided in \emph{aspects to maintain}, where strengths of teaching were identified, and \emph{targets for change}, where opportunities for improvement were identified.
\paragraph{Aspects to Maintain} The first strength Shahrukh identified was my use of questions and comprehension checks. He appreciated the variety of checks I used, as well as the split between content-specific checks and general purpose open-ended questions. He commented that ``\emph{All of this is
fantastic as it demonstrates a learner-centric approach to teaching rather than a teacher-centric
one. It shows that you want to take your learners along with you as the lesson progresses and
are willing to pause and clarify confusions before moving on.}''

@@

\subsubsection*{Second Teaching Observation}
\paragraph{}My second observation was conducted by Caelan Wang, a Graduate Educational Developer with the CTE. The lecture to be observed was one my regularly scheduled lectures as the instructor for Deterministic OR Models in Spring $2019$, covering cutting plane methods for solving integer programs. Caelan was especially qualified to observe this lecture since she was a graduate from the same department I am pursuing my PhD in, and knew the topic well.

>>>>

\subsection{Outside Lecture}
\paragraph{}
While time in lecture is critically important for student development the vast majority of student time is spent outside of lecture. I encourage students to continue learning outside of lecture by providing resources for them to ask questions and receive feedback, and by providing compelling assignment problems which encourage constant thinking and revision of the material. While I believe in using assignments and projects which require students to work outside of lecture time, I believe it is important to recognize that my courses are not the only courses students are taking during the term. Therefore a big component of my approach to teaching and learning outside of the lecture is balancing my desire to keep have students keep the course material front of mind on regular basis with the need to be respectful of my students' time and busy schedules.

\paragraph{} Opt-in engagement is a great way to give students learning opportunities outside the lecture environment without overloading there schedules. The classic office hours are an example of this. The great benefit of office hours is that they allow me to give attending students individualized attention and to target their specific needs. Office hours are great for clearing up student questions, but they also present an even greater opportunity to spur student interest in the subject. After clearing up student questions I try to take the opportunity to engage in conversation with the student about why they are taking the course, what their interests are, etc. This often will lead to interesting discussions that run well outside the scope of a particular course. These discussions are nevertheless incredibly important, since they help me learn about student goals (and give them a chance to articulate their goals) and let me open the student's eyes to the wider possibilities of what the subject can offer.

Office hours are not always convenient for students, and it's rare that timeslots can be found which work for every student. Some students are also anxious about talking face to face with their professor, and might prefer to discuss course material with other students. To faciliate this I use online discussion forums such as Piazza with my students. The teaching assistants and myself will monitor the forum to provide authoritative answers to student questions, but usually this amounts to nothing more than confirming a well-written reply by another student is in fact correct. These online forums help create a constant conversation between students on the course material while not putting too much burden on their schedules. To faciliate and encourage discussions, I will use the forums to have students create assignment solutions. After an assignment has been completed, a topic on the discusion board will appear for each question on the assignment. In that topic, the students are encouraged to discuss and crowdsource together the solution to the assignment problem. For more intricate or subtle questions I have found these topics to lead to a lot of stimulating conversation amongst the students.

\paragraph{}
\subsection{Assessment}

\paragraph{} \textit{Importance of spaced repetition for studying. Importance of priming students for lecture via problems. Assigment problems and timing}
\begin{itemize}
    \item Multi-modal assessments
    \begin{itemize}
        \item Classic problem sets
        \item Oral interviews
        \item Long term projects with group collaboration
        \item Mdterms and Final Exam with cheatsheet format.
    \end{itemize}
    \item Oral vs Written exams
    \item Importance of Collaboration and long term projects
    \item The cheatsheet format for exams and its benefits
\end{itemize}
\section{Evaluation of Teaching}
I find feedback on my teaching to be tremendously valuable. It is the easiest way for me to identify potential avenues for improvement, while at the same time motivating me by highlighting strong points of my teaching style. I have organized my evaluations below into two categories: those from students in courses I have taught, and those from peers and teaching professionals observing my lectures.
\subsection{Student Evaluations}
%Chart out survey responses for CO 327 with survey adjectives for context for scores (some here, rest in appendix)
%Student comment strong points
%Student comment targets for change
\subsection{Teaching Observations}
One element of the CUT teaching program I took alongside my PhD was having lectures I give upervised by an expert in teaching working with the university's Centre for Teaching Excellence (CTE). I completed two teaching observations through the program. Below I summarize the feedback I received from these observations.
%highlights from 1st observation
\subsubsection*{First Teaching Observation}
\paragraph{}
My first observation was on the guest lecture I gave for Introduction to Game Theory in Fall $2018$ on Correlated Equilibria. The observation was conducted by Shahrukh Athar, a Graduate Instructional Developer working for the CTE. I have included the relevant sections of the full report in Appendix \ref{sec:observation-report-1}. The feedback in the report was divided in \emph{aspects to maintain}, where strengths of teaching were identified, and \emph{targets for change}, where opportunities for improvement were identified.
\paragraph{Aspects to Maintain} The first strength Shahrukh identified was my use of questions and comprehension checks. He appreciated the variety of checks I used, as well as the split between content-specific checks and general purpose open-ended questions. He commented that ``\emph{All of this is
fantastic as it demonstrates a learner-centric approach to teaching rather than a teacher-centric
one. It shows that you want to take your learners along with you as the lesson progresses and
are willing to pause and clarify confusions before moving on.}''

@@

\subsubsection*{Second Teaching Observation}
\paragraph{}My second observation was conducted by Caelan Wang, a Graduate Educational Developer with the CTE. The lecture to be observed was one of my regularly scheduled lectures as the instructor for Deterministic OR Models in Spring $2019$, covering cutting plane methods for solving integer programs. Caelan was especially qualified to observe this lecture since she was a graduate from the same department I am pursuing my PhD in, and knew the topic well.
